Evolution of pre-copulatory and post-copulatory inbreeding behaviour \\ \vspace{10 mm} {\sffamily\Large\bfseries Supplemental results showing change in allele values over different parameter combinations, and allele values over generations for single replicates}

### 2017-04-05 Supplement.tex
Rearrange figures in the supplemental material

\noindent \textbf{Here we present supplemental results from an individual-based model in which alleles underlying polyandry (\bm{$P_{a}$}), pre-copulatory inbreeding strategy (\bm{$M_{a}$}) and post-copulatory inbreeding strategy (\bm{$F_{a}$}) affect evolving phenotypic values for each trait over 40000 generations. The first figure in this supplement summarises trajectories of allele values across replicate simulations for all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}). The second figure shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry. Remaining figures show the dynamics of individual replicate simulations for all trait cost combinations of \bm{$0$} and \bm{$0.02$}; these figures also show correlations of mean allele values among replicates.}

@@

\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S3}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S4}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S5}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S6}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S7}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S8}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S9}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S10}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S11}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S12}

>>>>

\noindent \textbf{Here we present supplemental results from an individual-based model in which alleles underlying polyandry (\bm{$P_{a}$}), pre-copulatory inbreeding strategy (\bm{$M_{a}$}) and post-copulatory inbreeding strategy (\bm{$F_{a}$}) affect evolving phenotypic values for each trait over 40000 generations. Figures S\ref{SI_M00_P00_E00}-S\ref{SI_M02_P02_E02} show the dynamics of individual replicate simulations for all trait cost combinations of \bm{$0$} and \bm{$0.02$}; these figures also show correlations of mean allele values among replicates. Figure S\ref{allcombs} summarises trajectories of allele values across replicate simulations for all cost combinations of \bm{$0$} and \bm{$0.02$} for polyandry (\bm{$c_{P}$}), pre-copulatory inbreeding strategy (\bm{$c_{M}$}), and post-copulatory inbreeding strategy (\bm{$c_{F}$}). Figure \ref{extra_MfPf} shows how \bm{$F_{a}$} alleles change over generations given that \bm{$M_{a}$} alleles are fixed for strong inbreeding avoidance and \bm{$P_{a}$} alleles are fixed for polyandry.}

@@

\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S3}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E00}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S4}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0$}}}{S5}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S6}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E00}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0$}}}{S7}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P00_E02}: Individual replicate results given \bm{$c_{P}=0$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S8}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M00_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0$}, \& \bm{$c_{F}=0.02$}}}{S9}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{SI_M02_P02_E02}: Individual replicate results given \bm{$c_{P}=0.02$}, \bm{$c_{M}=0.02$}, \& \bm{$c_{F}=0.02$}}}{S10}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{allcombs}: All cost combinations}}{S11}
\contentsline {section}{\tocsection {}{}{\small Figure S\ref{extra_MfPf}: Dynamic \bm{$F_{a}$}, fixed \bm{$P_{a}=1$} and \bm{$M_{a}=-10$}}}{S12}
